``Interestingness'' in Mathematical Theory Exploration

### 2019-10-18 PhDThesis/litreview_staticanalysis.tex
Fix tex

A more speculative use of optimisation during runtime has been proposed by
Hutter~\iffalse TODO: Cite \fi. As in a JIT-enabled interpreter, Hutter's
algorithm (also referred \hsearch{}) begins by directly executing the given
(unoptimised) program $p$ on the relevant input $x$ (this may be provided up
front, or piecemeal throughout execution, e.g. as a stream of user interaction
events). The variables $p_{fast}$ and $t_{fast}$ are initialised to $p$ and
$\infinity$ respectively, to indicate that $p$ is the fastest implementation we
have so far, and we don't yet have an upper bound on its running
time. Concurrently with the execution of $p$, two other processes are also
started:

>>>>

A more speculative use of optimisation during runtime has been proposed by
Hutter~\iffalse TODO: Cite \fi. As in a JIT-enabled interpreter, Hutter's
algorithm (also referred \hsearch{}) begins by directly executing the given
(unoptimised) program $p$ on the relevant input $x$ (this may be provided up
front, or piecemeal throughout execution, e.g. as a stream of user interaction
events). The variables $p_{fast}$ and $t_{fast}$ are initialised to $p$ and
$\infty$ respectively, to indicate that $p$ is the fastest implementation we
have so far, and we don't yet have an upper bound on its running
time. Concurrently with the execution of $p$, two other processes are also
started:
